Two years of CiTO annotations

### 2022-08-28 article.Rmd
Table captions done right too now

**Table 1**: *Journal of Cheminformatics* articles in the first year of the pilot.

@@

**Table 2**: *Journal of Cheminformatics* articles in the second year of the pilot. The * indicates that
the percentage is based on CiTO intends different from cito:cites.

@@

>>>>

@@

Table: *Journal of Cheminformatics* articles in the first year of the pilot.

@@

Table: *Journal of Cheminformatics* articles in the second year of the pilot. The * indicates that
the percentage is based on CiTO intends different from cito:cites.
